%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Simple LaTeX CV Template %%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% NOTE: If you find that it says                                     %%
%%                                                                    %%
%%                           1 of ??                                  %%
%%                                                                    %%
%% at the bottom of your first page, this means that the AUX file     %%
%% was not available when you ran LaTeX on this source. Simply RERUN  %%
%% LaTeX to get the ``??'' replaced with the number of the last page  %%
%% of the document. The AUX file will be generated on the first run   %%
%% of LaTeX and used on the second run to fill in all of the          %%
%% references.                                                        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't like 10pt? Try 11pt or 12pt
\documentclass[10pt]{article}

% This is a helpful package that puts math inside length specifications
\usepackage{calc}

% Simpler bibsection for CV sections
% (thanks to natbib for inspiration)
\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}
    {\minipage[t]{\linewidth}\list{}{%
        \setlength{\leftmargin}{\bibhang}%
        \setlength{\itemindent}{-\leftmargin}%
        \setlength{\itemsep}{\bibsep}%
        \setlength{\parsep}{\z@}%
        }}
    {\endlist\endminipage}
\makeatother

% Layout: Puts the section titles on left side of page
\reversemarginpar

%
%         PAPER SIZE, PAGE NUMBER, AND DOCUMENT LAYOUT NOTES:
%
% The next \usepackage line changes the layout for CV style section
% headings as marginal notes. It also sets up the paper size as either
% letter or A4. By default, letter was used. If A4 paper is desired,
% comment out the letterpaper lines and uncomment the a4paper lines.
%
% As you can see, the margin widths and section title widths can be
% easily adjusted.
%
% ALSO: Notice that the includefoot option can be commented OUT in order
% to put the PAGE NUMBER *IN* the bottom margin. This will make the
% effective text area larger.
%
% IF YOU WISH TO REMOVE THE ``of LASTPAGE'' next to each page number,
% see the note about the +LP and -LP lines below. Comment out the +LP
% and uncomment the -LP.
%
% IF YOU WISH TO REMOVE PAGE NUMBERS, be sure that the includefoot line
% is uncommented and ALSO uncomment the \pagestyle{empty} a few lines
% below.
%

%% Use these lines for letter-sized paper
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=0.75in,               % 1 inch margins
            includemp]{geometry}

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactitem will be nice.
\usepackage{paralist}

%% Reference the last page in the page number
%
% NOTE: comment the +LP line and uncomment the -LP line to have page
%       numbers without the ``of ##'' last page reference)
%
% NOTE: uncomment the \pagestyle{empty} line to get rid of all page
%       numbers (make sure includefoot is commented out above)
%
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The title (name) with a horizontal rule under it
%
% Usage: \makeheading{name}
%
% Place at top of document. It should be the first thing.
\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\large \bfseries #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}

% The section headings
%
% Usage: \section{section name}
%
% Follow this section IMMEDIATELY with the first line of the section
% text. Do not put whitespace in between. That is, do this:
%
%       \section{My Information}
%       Here is my information.
%
% and NOT this:
%
%       \section{My Information}
%
%       Here is my information.
%
% Otherwise the top of the section header will not line up with the top
% of the section. Of course, using a single comment character (%) on
% empty lines allows for the function of the first example with the
% readability of the second example.
\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \scshape #1}#2}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactitem}[#1]}{\end{compactitem}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[2]}

% 

%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
% NOTE: Mind where the & separators and \\ breaks are in the following
%       table.
%
% ALSO: \rcollength is the width of the right column of the table
%       (adjust it to your liking; default is 1.85in).
%

\begin{document}
\makeheading{LCDR Carl A.~Pearson, Ph.D.}

\section{Contact Information}
\newlength{\rcollength}\setlength{\rcollength}{1.95in}%
%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
\href{http://www.epi.ufl.edu/}%
     {Emerging Pathogens Institute} & \\
\href{http://www.ufl.edu/}{University of Florida}
                           & \textit{Cell:} (202) 360-9460 \\
P.O. Box 100009            & \textit{Fax:} (352) 273-6890 \\
2055 Mowry Road           & \href{mailto:cap10@ufl.edu}{cap10@ufl.edu}\\
Gainesville, FL 32610    & \\ %\href{http://sites.google.com/site/cabpearson/}{sites.google.com/site/cabpearson/}\\
\end{tabular}

%\section{Security Clearance}
%
%Department of Defense Top Secret SCI with polygraph (expired: 2002)

%\section{Citizenship}
%
%USA

\section{Research Interests}
%
Analytical and computational modeling of dynamic systems, and development of software pipelines to improve and promote more widespread use of these models

\section{Education}
%
\href{http://www.gwu.edu/}{\textbf{The George Washington University}},
Washington, DC
\begin{outerlist}

\item[] Ph.D.,
        \href{http://www.phys.gwu.edu/}
             {Physics}
             (Jan 2012); M.Phil., Physics (May 2010)
        \begin{innerlist}
        \item Thesis Topic: \emph{Complex System Ensemble Analysis}
        \item Advisers: Professors
              \href{http://home.gwu.edu/~chenz/}
                   {Chen Zeng} (Physics), 
              \href{http://www.seas.gwu.edu/~simha/}
                   {Rahul Simha} (Computer Science)
        \end{innerlist}
        

\end{outerlist}

\blankline

\href{http://www.nps.edu/}{\textbf{The Naval Post-Graduate School}},
Monterey, CA
\begin{outerlist}

\item[] M.S.E.S,
        \href{http://www.nps.edu/Academics/GSEAS/MAE/}
             {Mechanical Engineering}
             (Apr 2006)
        \begin{innerlist}
        \item Thesis Topic: \emph{Nuclear Submarine Reactor and Engineering Spaces Design Study}
        \item Specialization: Thermal Hydraulics
        \item Adviser: Dr. G. Hay, \href{http://www.bettislab.com/}{Bettis Atomic Power Laboratory}
        \end{innerlist}
\end{outerlist}

\blankline

\href{http://www.duke.edu/}{\textbf{Duke University}},
Durham, NC
\begin{outerlist}

\item[] B.S.
        \href{http://www.math.duke.edu/}{Mathematics},
        \href{http://www.phy.duke.edu/}{Physics},
        \href{http://philosophy.duke.edu/}{Philosophy (minor)} (May 2003)

        \begin{innerlist}
        \item Physics Independent Study Topic: \emph{Pyroelectric Effect}
        \item Adviser: \href{http://fds.duke.edu/db/aas/Physics/faculty/guenther}
                   {Professor Bob Guenther}
        \item Mathematics Independent Study Topic: \emph{Genetic Algorithm Optimization}
        \item Adviser: \href{http://fds.duke.edu/db/aas/Physics/faculty/rgb}
                   {Professor Robert Brown}
        \end{innerlist}
\end{outerlist}

\section{Professional Experience}
\href{http://www.epi.ufl.edu}{\textbf{University of Florida, Emerging Pathogens Institute}},
Gainesville, FL USA
\begin{innerlist}
\item[] \textit{Postdoctoral Researcher} \hfill \textbf{since Jan 2012}
\item[] Supervisor: \href{mailto:bhsinger@ufl.edu}{Burt Singer}
\end{innerlist}

\href{http://www.onr.navy.mil/en/Science-Technology/Naval-Reservists-p38.aspx}{\textbf{Office of Naval Research Reserve Component}}, Arlington, VA USA
\begin{innerlist}
\item[] \textit{Executive Officer}, ex-USS SHADWELL, NRL S\&T 117%
        \hfill \textbf{Aug 2011-Nov 2014}
\item[] \textit{Deputy Chief Information Officer}%
        \hfill \textbf{since Jul 2009}
\begin{innerlist}
\item Software Architect and Developer: \href{https://edison.nrl.navy.mil/}{\textbf{Edison}}
\end{innerlist}
\item[] \textit{Project Lead, \href{http://stdio-ghana.github.io}{STDIO Ghana Course}}%
        \hfill  \textbf{Oct 2012-present}
\item[] \textit{Project Coordinator, Automated Imaging Maritime Threat Analysis}%
        \hfill  \textbf{2010}
\item[] Commanding Officers: \href{mailto:PETER.M.GAMERDINGER@saic.com}{CAPT Peter Gamerdinger, USN}; \href{mailto:diane.boettcher1@navy.mil}{CAPT Diane Boettcher, USN}; \href{mailto:daniel.m.mirelez@navy.mil}{CDR Dan Mirelez, USN}; \href{mailto:alex.l.jones@navy.mil}{LCDR Alex Jones, USN}
\end{innerlist}

\href{http://nnsa.energy.gov/ourmission/poweringnavy\#hq}{\textbf{Naval Reactors}}, Washington, DC USA
\begin{innerlist}

\item[] \textit{Engineer, Reactor Systems Division}%
        \hfill \textbf{Mar 2004 to Sep 2008}
\begin{innerlist}
\item Reactor Lead: Next-Gen Aircraft Carrier, Attack Submarine Retro-fit, Next-Gen Ballistic Missile Submarine, Experimental and Training Prototype Platform
\item Supervisors: Group: \href{mailto:farberre@comcast.net}{Robert E. Farber, S.E.S (retired)}; \\Division: \href{mailto:skauffman@mpr.com}{Storm Kauffman, S.E.S (retired)}
\end{innerlist}

\item[] \textit{Engineer, Submarine Fluid Systems Division}%
        \hfill \textbf{Jul 2003 to Mar 2004}
\begin{innerlist}
\item Fluid Systems Lead, Prototype Reactor and Site Off-Hull Equipment
\item Supervisors: Group: Tom Boughner, S.E.S (retired); Gordon Baum (retired); \\ Division: CAPT Vic Mortenson, USN(r)
\end{innerlist}
\end{innerlist}

\section{Awards}
\href{http://www.navy.mil/}{United States Navy}
\begin{innerlist}
\item Navy-Marine Corps Commendation Medal, 2012, second citation Oct 2014
\item \href{https://www.nrotc.navy.mil/}{Reserve Officer Training Corps Scholarship}, 1999-2003
\end{innerlist}

\href{http://www.gwu.edu}{The George Washington University}
\begin{innerlist}
\item Chair's Prize for Graduate Research, 2012
\item \href{http://www.gwu.edu/~bulletin/grad/fnad.html}{Andrew John Knox Fellowship}, 2009-2011
\end{innerlist}

\href{http://www.math.duke.edu/}{Duke Mathematics Department}
\begin{innerlist}
\item Undergraduate Research Fellowship, 2001
\end{innerlist}

\href{http://www.duke.edu}{Duke University}
\begin{innerlist}
\item Dean's List, 1999
\end{innerlist}

\section{Grants} NSF/DEB Funding
\begin{innerlist}
\item RAPID: Understanding and leveraging asymptomatic Infections to control Ebola.  Recommended for funding, award of \$188,509 over 1 year pending. PI: J.R.C.\ Pulliam. Role: named postdoctoral researcher.
\end{innerlist}

\section{Publications} \begin{bibsection}
\item Heesterbeek, JAP, RM~Anderson, C~Dye, K~Eames, JC~Edmunds, S~Funk, DT~Hollingsworth, TA~House, V~Isham, J~Lessler, JO~Lloyd-Smith, CJE~Metcalf, L~Pellis, JRC~Pulliam, MG~Roberts, C~Viboud, and the Isaac Newton Institute Infectious Disease Dynamics Group ({\bf CAB~Pearson}). (Accepted) Modeling infectious disease dynamics in the complex landscape of global health. {\em Science}.
   \item {\bf CAB Pearson}, E Airoldi, and BH Singer.  ``Challenges to Understanding Covert Groups.''  {\em Illuminating Dark Networks: The Study of Clandestine Groups and Organizations}.  Ed. Luke~Gerdes.
Cambridge: Structural Analysis in the Social Sciences Series, Cambridge University Press, {\em in press}.
    \item {\bf CAB Pearson}, R Simha, C Zeng.  Network Class Superposition Analysis.\\
\href{http://www.plosone.org/article/info\%3Adoi\%2F10.1371\%2Fjournal.pone.0059046}{\emph{PLoS One}}, 2013.
    \item G. Wang, C. Zeng, R. Wong, R. Simha, H. Chen, {\bf C. Pearson}, and C. Du. Process-driven inference of biological network structure: feasibility, minimality, and multiplicity.\\
	 \href{http://www.plosone.org/article/info\%3Adoi\%2F10.1371\%2Fjournal.pone.0040330}{\emph{PLoS One}}, 2012.
\end{bibsection}

\section{Presentations \&{} Posters} \begin{bibsection}
\item JRC Pulliam and {\bf CAB Pearson}. Improving vector-based surveillance for mosquito-borne infections. {\em Ecological Society of America}. Sacramento, CA.  2014.
\item {\bf CAB Pearson}, BH Singer, and D Bright. Simulating Meth Production Networks\\
\emph{Sunbelt XXXIV}, St. Pete's Beach, FL.  2014.
\item RK Borchering, {\bf CAB Pearson}, AT Gilbert, JD Blanton, RM Wallace, and JRC Pulliam.
Assessing seasonal drivers of rabies dynamics in three North American carnivore species
\emph{Epidemics 4}, Amsterdam, NL.  2013.
\item {\bf CAB Pearson}, TJ Hladish. Epidemics on Dynamic, Empirical Networks\\
\emph{Epidemics 4}, Amsterdam, NL.  2013.
\item {\bf CAB Pearson}. Managing Your Physicist\\
\emph{Minerva Dark Networks Workshop}, West Point, NY.  2013.
\item {\bf CAB Pearson}, BH Singer, E Airoldi, and E Kao. Detection of Small Covert Networks Embedded in Large Networks\\
\emph{Sunbelt XXXIII}, Hamburg, DE.  2013.
\item JRC Pulliam, {\bf CAB Pearson}, JM Rowland, JS Lord, and BH Singer.
Japanese encephalitis virus in Japan: insights from dynamic models\\
\emph{EPI Research Day}, Gainesville, FL.  2013.
\end{bibsection}
\newpage
\section{Teaching Experience}\href{http://www.aims.edu.gh/}{\textbf{African Institute for Mathematical Sciences (AIMS) Ghana}}
\begin{outerlist}

\item[] \textit{\href{http://aims-ghana.github.io/python-course/}{Introduction to Scientific Computing with Python}}%
    \hfill \textbf{Sep 2014}
    \begin{innerlist}
            \item Developing syllabus and challenge material for Python
            \item On-going discussion with students
            \item Evaluating student performance, overseeing teaching assistant grading
            \item AIMS Ghana Academic Director: \href{mailto:prince@aims.edu.gh }{Prince Osei}
    \end{innerlist}
\end{outerlist}~


\href{http://www.onr.navy.mil/Science-technology/onr-global.aspx}{\textbf{Office of Naval Research, Global Division}}
\begin{outerlist}

\item[] \textit{\href{http://stdio-ghana.github.io/}{STDIO Ghana Course}}%
    \hfill \textbf{Oct 2012 to present}
    \begin{innerlist}
        \item Project Lead, Instructor for summer courses in 2013, 2014
        \begin{innerlist}
            \item Running on-going prep for two week intensive course on software development at University of Ghana
            \item Responsible for course material on several software engineering and language topics
            \item Project Sponsor: \href{mailto:vogela@onr.navy.mil }{Augustus Vogel} (Santiago, Chile Office)
        \end{innerlist}
    \end{innerlist}
\end{outerlist}~

\href{http://www.gwu.edu}{\textbf{The George Washington University}},
Washington, DC USA
\begin{outerlist}

\item[] \textit{Teaching Assistant}%
    \hfill \textbf{Sep 2008 to May 2009}
    \begin{innerlist}
    \item Instructor for PHY-21: \href{http://www.ncsu.edu/PER/scaleup.html}{SCALE-UP} Biologically-inspired Classical Mechanics, Spring Semester 2009
        \begin{innerlist}
            \item Lead Instructor: \href{http://www.gwu.edu/~condmat/CME/reeves.html}{Professor Mark Reeves}

            \item Helped run 6~hour in-class guided laboratory and problem-solving session with freshman and sophomore students; developed course materials, and analyzed students.
        \end{innerlist}~
        \item Lead Lab Instructor for PHY-22: Introduction to Electricity and Magnetism (Calculus-based), Fall Semester 2008
        \begin{innerlist}
        \item Lead Instructor: \href{http://physics.columbian.gwu.edu/andrei-alexandru}{Professor Andrei Alexandru}
            \item Ran 3~hour laboratory where freshman and sophomore undergraduate
                students complete pedagogical experiments, and 2~hour recitation and problem solving session
            \item Coordinated all evaluation (homework, exams, quizzes, etc)
        \end{innerlist}~

     \item Lab Instructor for PHY-12: Introduction to Electricity and Magnetism (Algebra-based), Fall Semester 2008
        \begin{innerlist}
	   \item Lead Instructor: \href{https://www.linkedin.com/pub/anna-micherdzinska/18/9a6/4a9}{Professor Anna Micherdzinska}
            \item Ran 3~hour laboratory where freshman and sophomore undergraduate
                students complete pedagogical experiments, and 2~hour recitation and problem solving session
        \end{innerlist}~

    \end{innerlist}
\end{outerlist}

\section{Service}
Open source contributor to various projects \\
Officer, United States Navy, since May 2003 \\
Technical Supervisor, \href{http://www.hoofnhorn.org/}{Hoof'n'Horn Musical Theater Company}, 2000-2003

\section{Technical Skills}
%
Broad experience with scientific and engineering frameworks, including development, use in parallel applications, and coordination with large databases

\blankline

Programming Skills: Scala, R, Python, Javascript, Perl, Java, C/C++, Pascal, FORTRAN, various SQLs, assorted frameworks and tools (version control systems, IDEs).  Web development using various frameworks and preprocessing languages.

\blankline

Experienced in carpentry, brazing, soldering, welding (stick and inert-gas), and bench-top machining.  Some experience with automated machining systems. Some experienced with Computer-Aided Design, Engineering, and Manufacturing.

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
